MCC Models

### 2019-03-12 papers/full_paper/models.Rmd
refactor parameter passing for adult ex4 to reduce chance of copy errors

```{r model setup ex 3 adults}
# create datafiles with model parameters
model_params_ex3 <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  speak_opt = adult_model_param$so_map)

prior_pref_same <- adult_ex2_preference_data %>%
  filter(condition == "same_speaker")%>%
  summarise(prior = mean(correct))

@@

```{r log likes ex3 adults}
# calculating model log-likelihoods
log_like_pragmatic_ex3 <- adult_ex3_data %>%
  left_join(ex3_pragm_model_predictions)%>%
  mutate(like = ifelse(correct_inf == "1",value,1-value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_flat_prior_ex3 <- adult_ex3_data %>%
  left_join(ex3_flat_prior_model_predictions)%>%
  mutate(like = ifelse(correct_inf == "1",value,1-value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_prior_only_ex3 <- adult_ex3_data %>%
  left_join(ex3_prior_only_model_predictions)%>%
  mutate(like = ifelse(correct_inf == "1",value,1-value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

@@

```{r bayes factors ex3 adults}
ex3_bf <- data.frame(
  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
  log_bayes_factor = c(
    log_like_pragmatic_ex3$model_log_like - log_like_flat_prior_ex3$model_log_like,
    log_like_pragmatic_ex3$model_log_like- log_like_prior_only_ex3$model_log_like,
    log_like_flat_prior_ex3$model_log_like - log_like_prior_only_ex3$model_log_like)
)

ex3_bf%>%
  kable(digits = 2)
```

@@

strongPrior <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("strong",8))

strong_prior_pref_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "strong",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_pref_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "strong",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "strong",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "strong",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

strongPrior$prior = list(
    c(1-strong_prior_pref_same$prior,1-strong_prior_pref_same$prior,strong_prior_pref_same$prior), 
    c(strong_prior_pref_same$prior,strong_prior_pref_same$prior,1-strong_prior_pref_same$prior), 
    c(1-strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior,strong_prior_pref_diff$prior), 
    c(strong_prior_pref_diff$prior,strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior),
    c(1-strong_prior_novel_same$prior,1-strong_prior_novel_same$prior,strong_prior_novel_same$prior), 
    c(strong_prior_novel_same$prior,strong_prior_novel_same$prior,1-strong_prior_novel_same$prior), 
    c(1-strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior,strong_prior_novel_diff$prior), 
    c(strong_prior_novel_diff$prior,strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior))

mediumPrior <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("medium",8))

medium_prior_pref_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "medium",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_pref_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "medium",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "medium",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "medium",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

mediumPrior$prior = list(
    c(1-medium_prior_pref_same$prior,1-medium_prior_pref_same$prior,medium_prior_pref_same$prior), 
    c(medium_prior_pref_same$prior,medium_prior_pref_same$prior,1-medium_prior_pref_same$prior), 
    c(1-medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior,medium_prior_pref_diff$prior), 
    c(medium_prior_pref_diff$prior,medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior),
    c(1-medium_prior_novel_same$prior,1-medium_prior_novel_same$prior,medium_prior_novel_same$prior), 
    c(medium_prior_novel_same$prior,medium_prior_novel_same$prior,1-medium_prior_novel_same$prior), 
    c(1-medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior,medium_prior_novel_diff$prior), 
    c(medium_prior_novel_diff$prior,medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior))

weakPrior <- data.frame(
  common_ground_manipulation = c("novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("weak",4))

weak_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "weak",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

weak_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "weak",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

weakPrior$prior = list(
    c(1-weak_prior_novel_same$prior,1-weak_prior_novel_same$prior,weak_prior_novel_same$prior), 
    c(weak_prior_novel_same$prior,weak_prior_novel_same$prior,1-weak_prior_novel_same$prior), 
    c(1-weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior,weak_prior_novel_diff$prior), 
    c(weak_prior_novel_diff$prior,weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior))

# combining all priors into one data frame
model_params_ex4 = rbind(strongPrior,mediumPrior,weakPrior)%>%
  mutate(speak_opt = adult_model_param$so_map)

@@

@@

@@

```{r correlation plot ex4 adults}

ex_4_cor_plot <- ex_4_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  mutate(data_mean = rep(ex_4_pred%>%filter(model == "data")%>%pull(mean),3),
         data_ci_lower = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_lower),3),
         data_ci_upper = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_upper),3))

@@

```{r loglikes ex4 adults}
# calculating model log-likelihoods
log_like_pragmatic_ex4 <- adult_ex4_data %>%
  left_join(ex4_pragm_model_predictions)%>%
  mutate(like = ifelse(correct_inf == "1",value,1-value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_flat_prior_ex4 <- adult_ex4_data %>%
  left_join(ex4_flat_prior_model_predictions)%>%
  mutate(like = ifelse(correct_inf == "1",value,1-value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_prior_only_ex4 <- adult_ex4_data %>%
  left_join(ex4_prior_only_model_predictions)%>%
  mutate(like = ifelse(correct_inf == "1",value,1-value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

@@

```{r bayes factors ex4 adults}
ex4_bf <- data.frame(
  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
  log_bayes_factor = c(
    log_like_pragmatic_ex4$model_log_like - log_like_flat_prior_ex4$model_log_like,
    log_like_pragmatic_ex4$model_log_like- log_like_prior_only_ex4$model_log_like,
    log_like_flat_prior_ex4$model_log_like - log_like_prior_only_ex4$model_log_like)
)

ex4_bf%>%
  kable(digits = 2)
```
# Children

>>>>

```{r model setup ex 3 adults}
# create datafiles with model parameters
model_params_ex3 <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  speak_opt = adult_model_param$so_map)
prior_pref_summary <- adult_ex2_preference_data %>%
  group_by(condition)
prior_pref_same <- adult_ex2_preference_data %>%
  filter(condition == "same_speaker")%>%
  summarise(prior = mean(correct))

@@

```{r log likes ex3 adults}
# calculating model log-likelihoods
log_like_pragmatic_ex3 <- adult_ex3_data %>%
  left_join(ex3_pragm_model_predictions)%>%
  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_flat_prior_ex3 <- adult_ex3_data %>%
  left_join(ex3_flat_prior_model_predictions)%>%
  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_prior_only_ex3 <- adult_ex3_data %>%
  left_join(ex3_prior_only_model_predictions)%>%
  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

@@

```{r bayes factors ex3 adults}

ex3_bf <- bind_rows(
  log_like_pragmatic_ex3,
  log_like_flat_prior_ex3,
  log_like_prior_only_ex3
) %>% spread(model, model_log_like) %>%
  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
         "pragmatic > prior_only" = pragmatic - prior_only,
         "flat_prior > prior_only" = flat_prior - prior_only) %>%
  select(-pragmatic,  -flat_prior, -prior_only)

ex3_bf %>%
  kable(digits = 2)
```

@@

strongPrior <- expand.grid(
  common_ground_manipulation = c("preference","novelty"),
  speaker = c("same_speaker","different_speaker"),
  prior_manipulation = c("strong", "medium", "weak")
)

strong_prior_summary <- adult_ex4_prior_data %>%
  group_by(common_ground_manipulation, prior_manipulation, speaker) %>%
  summarize(prior = mean(correct))

model_params_ex4 <- left_join( 
  strongPrior, 
  strong_prior_summary# %>% filter(prior_manipulation == "strong")
) %>%
  rename(congruent = prior) %>%
  mutate(incongruent = 1 - congruent) %>%
  gather(alignment, prior, congruent, incongruent) %>%
  drop_na() %>%
  mutate(speak_opt = adult_model_param$so_map)
```

@@

var output = map(function(row){
    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)

@@

    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: priorProbLst}));
      return obj.shape == "circle" ? 1 : 0
  }})

@@

```{r correlation plot ex4 adults}
ex_4_cor_plot <- ex_4_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  left_join(., ex_4_pred %>%
    ungroup()%>%
    filter(model == "data") %>%
    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
    select(-model)
  )

@@

```{r loglikes ex4 adults}
# calculating model log-likelihoods
log_like_pragmatic_ex4 <- adult_ex4_data %>%
  left_join(ex4_pragm_model_predictions)%>%
  mutate(like = ifelse(correct_inf == 1 , value, 1 - value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_flat_prior_ex4 <- adult_ex4_data %>%
  left_join(ex4_flat_prior_model_predictions)%>%
  mutate(like = ifelse(correct_inf ==  1, value , 1 - value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

log_like_prior_only_ex4 <- adult_ex4_data %>%
  left_join(ex4_prior_only_model_predictions) %>%
  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
         log_like = log(like))%>%
  group_by(model)%>%
  summarise(model_log_like = sum(log_like))

@@

```{r bayes factors ex4 adults}
ex4_bf <- bind_rows(
  log_like_pragmatic_ex4,
  log_like_flat_prior_ex4,
  log_like_prior_only_ex4
) %>% spread(model, model_log_like) %>%
  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
         "pragmatic > prior_only" = pragmatic - prior_only,
         "flat_prior > prior_only" = flat_prior - prior_only) %>%
  select(-pragmatic,  -flat_prior, -prior_only)

ex4_bf %>%
  kable(digits = 2)
```

# Children
